\chapter{Introduction}

% The Introduction should contain a description of your project and the
% problem you are trying to solve. It should start off at a level that
% should be understandable by anyone with a degree in physics, but it
% can become more technical later
%
% Where appropriate you should include references to work that has
% already been done on your topic and anything else which lets you set
% your work in context.
%
% One of the things you will need to do is to ensure that you have a
% suitable list of references.  To do this you should see \cite{Simon2013-lh}
% or some other suitable reference.  Note the format of the citation used
% here is the style favoured in this School.  Here is another
% reference \cite{Simon2013-lh} for good measure.
%
%
% You will also want to make sure you have no spelling or grammatical
% mistakes. To help identify speling mistukes you can use the commands
% \emph{aspell}, \emph{ispell} or \emph{spell} on most Linux/Unix
% computers. See the appropriate manual pages. Remember that spelling
% mistakes are not the only errors which can occur. Spelling checkers
% will not find errors which are, in fact, valid words such as
% \emph{there} for {\em their}, nor will they find repeated repeated
% words which sometimes occur if your concentration is broken when
% typing. \textbf{There is no substitute for thorough proof reading!}
%
% Your dissertation should be no longer than 15,000 words. In terms of
% pages, 30 pages are ok. 50 pages are fine. But it shouldn't be
% much longer than that.
%
%

% \input{Sections/MillerIndices.tex}
% \input{Sections/SpintronicMagnetometry}

% \section{Spectroscopy}


%% GENERAL GOOD REFS (Added to bib)
% Structural Analysis of Point Defects in Solids
% Point Defects in Semiconductors and Insulators: Determination of Atomic and Electronic Structure from Paramagnetic Hyperfine Interactions
% Electron Paramagnetic Resonance: Elementary Theory and Practical Applications

% \td{Need to make sure I find something from this one to avoid reference padding}
% Introduction to Magnetic Resonance with Applications to Chemistry and Chemical Physics



The field of spectroscopy studies the way atoms and molecules interact with and exchange energy with a wider physical system - specifically through electromagnetic radiation. The electric field interacts with with the electric dipole moment and the magnetic field interacts with a magnetic dipole moment.
Magnetic resonance spectroscopy focusses specifically on the interaction between the $\mathbf{B}$ field with magnetic moments which exist in a given material. This can be broken into two distinct fields:

\begin{description}
	\item [Nuclear Magnetic Resonance (NMR)] which studies the interaction with nuclear magnetic moments.
	\item [Electron Paramagnetic Resonance (EPR)] which studies the interaction with magnetic moments of electrons.
\end{description}

Using Planck's relationship $E = h \nu$  and $c = \lambda \nu$ we may characterise the electromagnetic radiation by its energy which is, to a constant, equivalent to the frequency or the wavelength. EPR is observed in systems where the magnetic dipole of the electron is influences by an applied, oscillating magnetic field forcing transitions between electron energy levels. In general the measurable difference in energy levels for which the transition occurs is caused by an external magnetic field via the Zeeman effect. Some systems also exhibit energy level splitting in the absence of an applied external magnetic field so called zero field splitting.

EPR is thus a tool to manipulate electron spins in solid state materials. The transition between energy levels is quantised thus the discrete amount of energy which is lost by the system is transferred into a photon or charge state which may be detected optically or electrically \cite{carrington1967introduction}.

A particularly successful technique is Optically Detected Magnetic Resonance (ODMR) which uses an applied microwave frequency, an oscillating magnetic field with energy quanta equivalent to the transitions between Zeeman sub levels, to drive the repopulation of those Zeeman sub levels following a spin-dependent optical transition.
In essence this boosts the sensitivity since the microwave driven repopulation induces a change in photoluminescence with a much higher and thus much more readily detectable energy. The techniques of ODMR are so effective that even a single electron spin may be detected this way \cite{Khler1993}.


Spintronics, a portmantau of \textbf{spin} and elec\textbf{tronics} is a technology which exploits the characteristics of spin akin to how charge is manipulated in electronics. Fundamentally, the smallest stable magnetic moment available in nature is generated by the spin of a single electron. If efficient read-out can be achieved, the sensitivity of the electron magnetic dipole cannot be matched. 
Careful construction of an appropriate system, or identification of a system with appropriate characteristics allows for the initialisation, manipulation and read-out of EPR from which we may infer the physical properties of the environment surrounding the system. 

% The ability to efficiently control spin states is the goal of semiconductor spintronics.  
The properties of nitrogen-vacancy (NV) colour centres in diamond have catalysed major development in the field.
The NV and ODMR have enabled the manipulation of spin states in single, atomic-sized centres at room temperature despite spin polariation being a primarily thermodynamic effect \td{need a reference for the thermodynamic comment}.
This is possible since optical excitation of the energy levels decay faster via a spin-preserving transition, leading to an inverse population of spin sublevels in its ground state when the system is irradiated consistently for several excitation/decay cycles.
Other structures with similar unique quantum properties are being identified. Specifically, Silicon carbide (SiC) is a promising candidate. A major benefit of SiC is the existence of various polytypes, which each exhibit unique spin colour centre properties. Furthermore, even within a single polytype, these centres can occupy distinct and non-equivalent lattice positions.
The existence of these colour centres with similar properties but different energy quanta allows for selection of a specific defect with parameters suitable for the problem at hand.

EPR can be approached by two different methods:
\tdg{Consider writing a paragraph on ENDOR - only if relevant later in the project.}
\begin{description}
	\item [Continuous Wave] the magnitude of the static magnetic field ($B_0$) is swept, while the
	      amplitude of the driving field $B_1$ is constant with time.
	\item [Pulsed] a time-dependent driving pulse $B_1$ is applied in
	      addition to a static magnetic field $B_0$.
	      \td{Need to write a section on using Pulsed EPR to measure relaxation timescales.}
\end{description}

This work looks to explore how the physical characteristics which influence the Hamiltonian, thus the energy, of the electron spin may be inferred by measuring the effects of those characteristics on EPR of the specific system. Further, it will look to explore whether the compound effect of multiple influences may be disentangled and distinguished simultaneously.




