\chapter{To Sort}
\input{Sections/Spin.tex}
\input{Sections/Zeeman.tex}
\input{Sections/HahnEcho.tex}
\input{Sections/Hyperfine.tex}
\input{Sections/SpinBaths.tex}
\input{Sections/SpinOrbit.tex}
\input{Sections/BohrMagneton.tex}
\input{Sections/SpinCoupling.tex}
\input{Sections/MillerIndices.tex}
\input{Sections/SpinDetection.tex}
\input{Sections/SpinRelaxation.tex}
\input{Sections/DensityMatrices.tex}
\input{Sections/MagneticDipoles.tex}
\input{Sections/RabiOscillations.tex}
\input{Sections/GyromagneticRatio.tex}
\input{Sections/SpinInitialisation.tex}
\input{Sections/LatticeSymmetry.tex}


\chapter{Task}
\section{Brief}

I think, as a start can go through section 3.2.4 in the attached PhD thesis? In particular check in details how to diagonalise the NV centre spin S=1 Hamiltonian to get Eq. 3.31?
You could also do some python simulations to plot how the spin levels (i.e. the eigenvalues of the spin Hamiltonian) change with applied magnetic field.

Once we've learned this, we can apply it to other spin defects in SiC.

\section{Work}
\subsection{Concepts and Nomenclature}
\subsubsection{Spin-Spin Interactions}
\subsubsection{Zeeman Splitting}
\subsubsection{Hyperfine Interaction}
\subsection{System Hamiltonian}\label{system_hamiltonian}
The ground state of the $\ce{NV^-}$ spin system in diamond is a triplet state, thus a $S=1$ system. 

The corresponding Hamiltonian, which it seems can be generalised to an electron spin system of a defect, can be expressed as: 
\begin{equation}
    H_{\ce{NV}} = H_{\ce{D}} + H_{\ce{Zeeman}} + H_{\ce{HF}} 
    \label{eq:nv_hamil}
\end{equation}

Here the labels $\ce{D}$, $\ce{Z}$ and $\ce{HF}$ describe the electron spin-spin interactions, the Zeeman interaction with an external magnetic field and the hyperfine interaction between the nuclparallel spin $I$ and the electron spin $S$ of the NV. 

They have the following forms: 
\begin{eqnarray}
    H_{\ce{D}} &=& D S_z^2 + E(S_x^2 + S_y^2) \label{H_D} \\
    H_{\ce{Z}} &=& g \mu_B \sum_{j}^{x,y,z} B_j \cdot S_j \label{H_Z} \\
    H_{\ce{HF}} &=& \vec{S} \cdot A \cdot \vec{I}. \label{H_HF}
\end{eqnarray}

\subsubsection{Spin-Spin Interaction}


The $E$ and $D$ in equation \ref{H_D} the fine structure constants of the spin
system, describing the spin-spin interaction and $S_j$ the corresponding spin operators
in x,y and z-direction. 

D is non-zero in system with axis of threefold (or other manifold) symmetry. 
The symmetry or spin quantization axis points along the connection of the nitrogen
atom and vacancy forming the defect. In bulk diamond $D$ is around 2.87 GHz at room temperature.

The definiteness, orientation and magnitude of $D$ is thus dependent on the specific spin system being studied. 

E occurs when there is a distortion of the point group symmetry, for example strain or an electrical field. In bulk diamond $E$ is typically negligibly small but especially in NDs, $E$ can be of the order of several MHz. 

Thus, similarly, the value of $E$ is a characteristic of the nature of the distortion and 
the specifics of the spin system being studied. 

\subsubsection{Zeeman Interaction}

$B_j$ in equation \ref{H_Z} is the magnetic field along the $x$, $y$ and $z$ direction, $g$ is the $g$-factor of the vacancy and $\mu_B$ the Bohr-Magneton, a constant. 

It seems often the scaled parameter $g\mu_B$ is considered, for the $\ce{NV^-}$ system this is around $28\;\ce{ GHz T^{-1}}$, but again, will be a characteristic of the system being studied. 

\subsubsection{Hyperfine Interaction}

Equation $\ref{H_HF}$ related the nuclear spin to the electron spin via the hyperfine tensor $A$ which has the form 
\begin{equation}
    A = \begin{pmatrix}
        A_\perp & 0 & 0 \\ 
        0 & A_\perp & 0 \\ 
        0 & 0 & A_\parallel
    \end{pmatrix}.
    \label{eq:hyperfine_tensor}
\end{equation}

$A_\parallel$ and $A_\perp$ are the axial and non-axial hyperfine parameters which encode two different interactions. 

\paragraph{Fermi Contact Interaction.}
This interaction is calculated by 
\begin{equation}
    f_A = \frac{A_\parallel + 2 A_\perp}{3}.
    \label{eq:fermi_contact}
\end{equation}

\paragraph{Anisotropic Interaction.}
This interaction is found by considering both spins as magnetic dipoles is calculated by 
\begin{equation}
    d_A = \frac{A_\parallel - A_\perp}{3}.
    \label{eq:anisotropic}
\end{equation}

For the $\ce{NV^-}$ system in diamond specifically, using the values for $A_\parallel$ and $A_\perp$ we calculate that $f_A$ is an order of magnitude stronger than $d_A$ for both $\ce{N^{14}}$ and $\ce{N^{15}}$. 

\subsubsection{Reduced Hamiltonian}
By combining $H_{\ce{D}}$ and $H_{\ce{Z}}$ 
and neglecting $H_{\ce{HF}}$ \todo{why (specifically) do we get to neglect this? Can we generalise?}
we find 
\begin{equation}
    H_{\ce{NV}} = D S_z^2 + E(S_x^2 + S_y^2) + g \mu_B \sum_{j}^{x,y,z} B_j \cdot S_j 
    \label{eq:reduced_H_NV}
\end{equation}

The spin operators $S_j$ in matrix representation are 
\begin{equation}
    S_x = \frac{1}{\sqrt{2}} \begin{pmatrix}
        0 & 1 & 0 \\ 
        1 & 0 & 1 \\ 
        0 & 1 & 0
    \end{pmatrix}, 
    S_y = \frac{i}{\sqrt{2}} \begin{pmatrix}
        0 & -1 & 0 \\ 
        1 & 0 & -1 \\ 
        0 & 1 & 0
    \end{pmatrix}, 
    S_z = \frac{1}{\sqrt{2}} \begin{pmatrix}
        1 & 0 & 0 \\ 
        0 & 0 & 0 \\ 
        0 & 0 & -1
    \end{pmatrix}. 
    \label{eq:spin_operators}
\end{equation}

Then, aligning the magnetic field (with strength $B_0$) along the $z$-axis (the quantisation axis), the reduced Hamiltonian will have the form 
\begin{equation}
    H_{\ce{NV}} = \begin{pmatrix}
        D + B_0 & 0 & E \\ 
        0 & 0 & 0 \\ 
        E & 0 & D-B_0
    \end{pmatrix},
    \label{eq:reduced_H_NV_matrix}
\end{equation}

with Eigenvalues 

\begin{equation}
    E_x = E_y = D \pm \sqrt{B_0^2  + E^2}, \; E_z = 0.
    \label{eq:reduced_H_NV_eigenvalues}
\end{equation}

The corresponding non-normalised Eigenvectors are then 

\begin{eqnarray}
    \ket{X} = \frac{1}{E} \left(B_0 + \sqrt{B_0^2 + E^2}\right) \ket{+1} + \ket{-1} \\ 
    \ket{Y} = \frac{1}{E} \left(B_0 - \sqrt{B_0^2 + E^2}\right) \ket{+1} + \ket{-1} \\ 
    \ket{Z} = \ket{0},
\end{eqnarray}
with
\begin{equation}
    \ket{1} = \begin{pmatrix}
        1 & 0 & 0 
    \end{pmatrix}, \; 
    \ket{0} = \begin{pmatrix}
        0 & 1 & 0 
    \end{pmatrix}\;, 
    \ket{-1} = \begin{pmatrix}
        0 & 0 & 1 
    \end{pmatrix},
    \label{eq:base_states}
\end{equation}
the Eigenvectors for $H_{\ce{NV}}$ with $E=0$\dots

In the case where $E \ll B_0$ the Eigenvectors are well described by the bases $\ket{0}$ and $\ket{\pm 1}$.

For $E \gg B_0$, when transforming the spin operators $S_j$ into the diagonalised system with Hamiltonian $H_{\ce{NV}}$ they read 
\begin{equation}
    \hat{S}_x^\parallel \propto \begin{pmatrix}
        0 & 1 & 0 \\ 
        1 & 0 & 0 \\ 
        0 & 0 & 0 
    \end{pmatrix} \; , 
    \hat{S}_y^\parallel \propto \begin{pmatrix}
        0 & 0 & 0 \\ 
        0 & 0 & -i \\ 
        0 & i & 0 
    \end{pmatrix} \; , 
    \hat{S}_z \propto \begin{pmatrix}
        0 & 0 & -1 \\ 
        0 & 0 & 0 \\ 
        -1 & 0 & 0 
    \end{pmatrix} , 
    \label{eq:diagonalised_spin_operators}
\end{equation}
and 
\begin{equation}
    \hat{H}_{\ce{NV}} = \begin{pmatrix}
        D + \sqrt{B_0^2 + E^2} & 0 & 0 \\ 
        0 & 0 & 0 \\ 
        0 & 0 & D - \sqrt{B_0^2 - E^2}. 
    \end{pmatrix} 
\end{equation}

Another solution for a $\pi/2$ shifted, modulating magnetic field leads to 
\begin{equation}
    \hat{S}_x^\perp \propto \begin{pmatrix}
        0 & 0 & 0 \\ 
        0 & 0 & 1 \\ 
        0 & 1 & 0 
    \end{pmatrix} \; , 
    \hat{S}_y^\perp \propto \begin{pmatrix}
        0 & -i & 0 \\ 
        i & 0 & 0 \\ 
        0 & 0 & 0 
    \end{pmatrix} \; , 
    \hat{S}_z \propto \begin{pmatrix}
        0 & 0 & 1 \\ 
        0 & 0 & 0 \\ 
        1 & 0 & 0 
    \end{pmatrix} , 
    \label{eq:diagonalised_spin_operators}
\end{equation}
a physical interpretation of which is that a linear modulating B-field aligned
along the $x$-axis where strain is applied only allows transitions between the state
$\ket{X}$ and $\ket{0}$, whereas fields perpendicular to the strain and the NV quantization axis
only allow coupling between $\ket{Y}$ and $\ket{0}$.

For an arbitrary external magnetic field, $H_\ce{NV}$ can be expressed using spherical co-ordinates: 
\begin{equation}
    H_{\ce{NV}} = \begin{pmatrix}
        D + B_0 \cdot \cos \theta & \frac{B_0}{\sqrt{2}} \cdot e^{-i\cdot \varphi} \cdot \sin\theta & E \\ 
        \frac{B_0}{\sqrt{2}} \cdot e^{i \cdot \varphi} \cdot \sin\theta & 0 & \frac{B_0}{\sqrt{2}} e^{-i\cdot \varphi} \cdot \sin\theta \\ 
        E & \frac{B_0}{\sqrt{2}} \cdot e^{i \cdot \varphi} \cdot \sin\theta & D - B_0 \cdot \cos \theta
    \end{pmatrix}
    \label{eq:nv_hamil_spherical_matrix}
\end{equation}


Here, we transformed the magnitude of the arbitrary magnetic field into spherical co-ordinates as 
\begin{eqnarray}
    B_x  &=& B_0 \cos\varphi \sin\theta \\ 
    B_y  &=& B_0 \sin\varphi \sin\theta \\ 
    B_z  &=& B_0 \cos\theta 
\end{eqnarray}
with $\theta$ the azimuthal and $\varphi$ the polar angle. Then using equations \ref{eq:reduced_H_NV} and \ref{eq:spin_operators} we compute \ref{eq:nv_hamil_spherical_matrix}.  

It immediately follows from the characteristic equation that Eigenvalues $\lambda$ satisfy 
\begin{equation}
    0 = \lambda^3 - 2\cdot \lambda^2 \cdot D + \frac{D \cdot B_0^2}{2} + \lambda(D^2 - E^2 - B_0^2) - \frac{1}{2}B_0^2\underbrace{\left(D \cdot \cos(2\theta) - 2 \cdot E \cos(2\varphi) \cdot \sin(\theta)^2\right)}_{\Delta_{\varphi \theta}}
    \label{eq:nv_spherical_characteristic_equation}
\end{equation}
% \cite{balasubramanian2009}




